GA-based Training-Free NAS Algorithm with Hybrid Score Function

### 2023-03-14 paper/main.tex

    Mellor et al. \cite{https://doi.org/10.48550/arxiv.2006.04647} proposed a 
    score function without the requirement for training. 
    Consider a mini-batch of data $X=\{x_i\}^N_{i=1}$ mapped through a neural 
    network as $f(x_i)$. The indicator variables from each ReLU units in $f$ 
    at $x_i$ form a binary code $c_i$ that define the linear region.
    The correlation between binary codes for the whole mini-batch can be examined 
    by computing the kernel matrix
    \begin{equation}
        K_H=\begin{pmatrix}N_A-d_H(c_1,c_2)&\cdots&N_A-d_H(c_1,c_N)\\\vdots&\ddots&\vdots\\N_A-d_H(c_N,c_1)&\cdots&N_A-d_H(c_N,c_1)\end{pmatrix}
    \end{equation}
    where $N_A$ is the number of ReLU units and $d_H(c_i,c_j)$ is the hamming 
    distance between the binary code $c_i$ and $c_j$.
    With the kernel matrix, the score of an architecture can be evaluate as 
    follow:
    \begin{equation}
        s=\log\lvert K_H\rvert
    \end{equation}
    The rationale behind is to see how dissimilar the linear region activated by 
    the ReLU units between two inputs. An architecture shall learn better 
    when inputs are well separated.
    Later, Wu et al. \cite{10.1145/3491396.3506510}

    On the other hand, instead of using the correlation of binary activation 
    patterns as score. Chen et al. proposed using the condition number of NTK 
    as an evaluation of the trainability, defined as
    \begin{equation}
        \mathcal{K_N}=\frac{\lambda_{\textrm{max}}(\hat\Theta)}{\lambda_{\textrm{min}}(\hat\Theta)}
    \end{equation}
    where $\lambda_{\textrm{max}}(\hat\Theta)$ and $\lambda_{\textrm{min}}(\hat\Theta)$ 
    are the maximum and minimum eigenvalues of NTK ($\hat\Theta$) respectively.
    The rationale behind is based on the work of Lee et al. \cite{Lee_2020} and 
    Xiao et al. \cite{DBLP:journals/corr/abs-1912-13053}, which concluded briefly, 
    the training dynamics of a wide neural network can be solved as 
    \begin{equation}
        \mu_t(\textbf{X}_{\textrm{train}})=(\textbf{I}-e^{-\eta\hat\Theta_{\textrm{train}}t})\textbf{Y}_{\textrm{train}}
    \end{equation}

>>>>

    Mellor et al. \cite{https://doi.org/10.48550/arxiv.2006.04647} proposed a 
    score function without the requirement for training. 
    Consider a mini-batch of data $X=\{x_i\}^N_{i=1}$ mapped through a neural 
    network as $f(x_i)$. The indicator variables from each ReLU units in $f$ 
    at $x_i$ form a binary code $c_i$ that define the linear region.
    The correlation between binary codes for the whole mini-batch can be examined 
    by computing the kernel matrix
    \begin{equation}
        K_H=\begin{pmatrix}N_A-d_H(c_1,c_2)&\cdots&N_A-d_H(c_1,c_N)\\\vdots&\ddots&\vdots\\N_A-d_H(c_N,c_1)&\cdots&N_A-d_H(c_N,c_1)\end{pmatrix}
    \end{equation}
    where $N_A$ is the number of ReLU units and $d_H(c_i,c_j)$ is the hamming 
    distance between the binary code $c_i$ and $c_j$.
    With the kernel matrix, the score of an architecture can be evaluate as 
    follow:
    \begin{equation}
        s=\log\lvert K_H\rvert
    \end{equation}
    The rationale behind is to see how dissimilar the linear region activated by 
    the ReLU units between two inputs. An architecture shall learn better 
    when inputs are well separated.
    Based on the work of Mellor et al., Wu et al. \cite{10.1145/3491396.3506510} 
    found, in some case, an architecture with high NASWOT score may put different 
    input data, which are originally in the same class, to different classes.

    To fix this defect, Wu et al. proposed using noise immunity to additionally 
    evaluate an architecture. The score function first pick a mini-batch of data, 
    denoted $X$, and then add Gaussion noise on it, denoted $X'$ and defined by $X'=X+z$ 
    where $z$ is the Gaussion noise. By passing $X$ and $X'$ through the untrained 
    architecture, the sum of the square differences between outputs 
    $O=\begin{matrix}o_1,o_2,\cdots,o_C\end{matrix}$ and 
    $O'=\begin{matrix}o_1',o_2',\cdots,o_C'\end{matrix}$ can be calculated as 
    follows:
    \begin{equation}
        n=-\sum^C_{n=1}(o_i-o_i')^2
    \end{equation}
    where $C$ is the number of classes determined by the input data.

    On the other hand, instead of using the correlation of binary activation 
    patterns as score. Chen et al. proposed using the condition number of NTK 
    as an evaluation of the trainability, defined as
    \begin{equation}
        \mathcal{K_N}=\frac{\lambda_{\textrm{max}}(\hat\Theta)}{\lambda_{\textrm{min}}(\hat\Theta)}
    \end{equation}
    where $\lambda_{\textrm{max}}(\hat\Theta)$ and $\lambda_{\textrm{min}}(\hat\Theta)$ 
    are the maximum and minimum eigenvalues of NTK ($\hat\Theta$) respectively.
    The rationale behind is based on the work of Lee et al. \cite{Lee_2020} and 
    Xiao et al. \cite{https://doi.org/10.48550/arxiv.1912.13053}, which concluded briefly, 
    the training dynamics of a wide neural network can be written in terms of the 
    spectrum of the NTK:
    \begin{equation}\label{eq:6}
        \mu_t(\textbf{X}_{\textrm{train}})_i=(\textbf{I}-e^{-\eta\lambda_it})\textbf{Y}_{\textrm{train,}i}
    \end{equation}
    where $\lambda_i$ are the eigenvalues of $\hat\Theta_{\textrm{train}}$ 
    and they're ordered as $\lambda_0\geq\cdots\geq\lambda_m$. 
    According to the hypothesis proposed by Lee et al. \cite{Lee_2020}, the maximum 
    feasible learning rate scale as $\eta\sim2/\lambda_0$. Plug this scaling for 
    $\eta$ in Eq. \ref{eq:6}, we see that the $\lambda_m$ will converge exponentially 
    at a rate given by $1/K_N$ where $K_N=\frac{\lambda_0}{\lambda_m}$.
    Then it can be concluded that if $K_N$ is lower, the corresponding architecture is 
    more trainable.
